\textls[-0]{\thetitle}

### 2023-03-23 stlc-linkage-typing-named.tex
more bugfixes
fix
Adding boldP computation.

\lsig_1 \coloneqq \LSigAdd{\lsig_0}{\seal_1}{

@@

@@

\lsig_2 \coloneqq \LSigAdd{\lsig_1}{\seal_2}{

@@

    \Wsup{}{\wsig_{\texttt{tm}}}{\top}{\bot}

@@

\lsig_6 \coloneqq \LSigAdd{\lsig_5}{\seal_6}{

@@

\lsig_{10} \coloneqq \LSigAdd{\lsig_9}{\seal_{10}}{

@@

\caption{\TT encoding of the \texttt{STLC} family from \cref{fig:stlc-mechanized}.
Each row $\goodTerm{\mathit{self}\!:\!
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i-cap}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i-cap}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i-cap}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i-cap}%
}$ types a field.
The type $A_i$ controls how the typing of field $t_i$ sees the types of the fields prior to $t_i$.
}
\label{fig:stlc-linkage-typing}
\end{figure}

>>>>

\lsig_1 \coloneqq \LSigAdd{\lsig_0}{x.\seal_1}{
    \mathit{self}\!.\,

@@

    \mathit{self}\!.\,

@@

\lsig_2 \coloneqq \LSigAdd{\lsig_1}{x.\seal_2}{
    \mathit{self}\!.\,

@@

    \Wsup{}{\wsig_{\texttt{tm}}}{\top}{x.\bot}

@@

\lsig_6 \coloneqq \LSigAdd{\lsig_5}{x.\seal_6}{
    \mathit{self}\!.\,

@@

\lsig_{10} \coloneqq \LSigAdd{\lsig_9}{x.\seal_{10}}{
    \mathit{self}\!.\,

@@

\begin{tabular}{ll}
  \hline
  $\TyTkg{\lsig_1} = \nTySigma{\_}{\top}{\TyS{\wcode{\wsig_{\texttt{tm}}}}} $ &  
  $\TyTkg{\lsig_2} = \nTySigma{\_}{\TyTkg{\lsig_1}}{\El{\wcode{\wsig_{\texttt{tm}}}}}$ \\  
  $\TyTkg{\lsig_6} = \nTySigma{P_5}{\TyTkg{\lsig_5}}{\CaseSig{\top}{\bot}{\El{P_5.tm} \to \mathit{id} \to \El{P_5.tm}}}$\EDJ{It strike me that, we don't have field projection for dependent tuple... so it is a bit ambiguous. I am not sure if I should continue; but some explanation of this field projection is required I believe} & \\ 
  $\TyTkg{\lsig_{10}} = \nTySigma{\_}{\TyTkg{\lsig_9}}{\El{\wcode{\wsig_{\texttt{tm}}}} \to \El{\wcode{\wsig_{\texttt{tm}}}} \to \mathit{id} \to \El{\wcode{\wsig_{\texttt{tm}}}}}$ & \\ 
\caption{\TT encoding of the \texttt{STLC} family from \cref{fig:stlc-mechanized}.
Each row $\goodTerm{\mathit{self}\!:\!
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i-cap}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i-cap}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i-cap}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i-cap}%
}$ types a field.
The type $A_i$ controls how the typing of field $t_i$ sees the types of the fields prior to $t_i$.
\label{fig:stlc-linkage-typing}

\end{figure}
